\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{url}
\usepackage[pagebackref,breaklinks,colorlinks]{hyperref}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Literature Review for Comps Project}

\author{Samuel Sanchez\\
COMP 390\\
Occidental College\\
{\tt\small sanchezs@oxy.edu}
}
\maketitle


%%%%%%%%% BODY TEXT
\section{Problem Context}
\label{sec:Prob Context}

For the project that I am doing, I want to make it easier for people that look at sports statistics to visualize the data on graphs to evaluate players. This will be a website or web app that can help people analyze sports players for fantasy sports that helps them pick the best player of their choice for their chosen stats. The user would be able to pick and group stats of the sport they are playing fantasy in and pick a player the want to compare those stats to. A scatter graph will be created to show where the player's data is at and if other players have similar stats. The stats used for the graph will also be in a chart below the graph to see the data. The user would be able to visualize and evaluate the players that are similar to the chosen player and decide on if they would use the player in fantasy sports for their team. The way the user picks that stats will also have a description of how the stat chosen is calculated to give more detail because a person might not know how it is calculated and what is used to calculate it. An example would be True Shooting stat in basketball and would read "TS\% stands for True shooting percentage and it is a measure of shooting efficiency that takes into account field goals, 3-point field goals, and free throws". It will also help users that are interested in sports analytics because of how the app will be a unique way of combining stats to visualize a spectrum of where players line up against each other. It will also be different compared to other databases because of the ability to include stats like body height, weight and age to evaluate players. 
    
There are no fantasy sports apps that analyzes stats that the users pick specifically and displays it on a graph. Fantasy apps currently only display stats on data charts which makes it hard to virtually analyze stats. Being able to visualize stats and players with specific stats chosen will help any fantasy team owner when picking players for their team. The help will come when a fantasy team owner wants to get a player that is similar to another player statistically and it will help generate points for the team over the season. When the best players are chosen by other teams, it gets harder to find players that produce the same amount of fantasy points and this will help target stats that produce points. Being able to group important stats together will help the owner to see how good other players are to a player that does well in the sport. The graph will show a correlation of the stats picked for evaluation, and it will help drive a decision of what player to pick for the team. 

%%%%%%%%% BODY TEXT
\section{Technical Background}
\label{sec:tech background}

For my approach of doing this project, I need to learn how to create a website that can query data from sports stats websites like \url{https://www.sports-reference.com/} and
\url{https://www.espn.com/}. When querying the data it will allow the user to gather those stats from the database websites and create a graph based on the chosen stats. I would have to learn how to create graphs from the gathered data using Python or another coding language that can create graphs. I would need to use an algorithm that can group stats together and make plots on a graph that uses the stats for each player that is being compared. The mathematical equations used would have to be programmed to be implemented when creating the graph based on that stats chosen and might require an algorithm to do it. When the mouse is over the data point, it would have to be programmed to show the player's name on the point. Below the graph would also show the stats used in a chart with other players names. This could be done with querying to select stats from the sports statistic websites and display them on a chart generated from the query. For selecting stats and the player, I would have to program the website to have drop down lists that display all the possible options to choose from.




%-------------------------------------------------------------------------

%%%%%%%%% BODY TEXT
\section{Prior Work}
\label{sec:prior work}

The prior work that has been done is a website called "NBA Player Performance and Scouting Explorer" and the website is \url{https://dash.gallery/bball-player-explorer/}. It is designed to be used as a way to view and group NBA players with stats on graphs. One of the graphs uses body weight and height as a way to group players with higher physicality or you can group the player strictly off statistics. The players are grouped in the graph based on their position in basketball and a player is selected to be compared to with a chart listed below the graph with the stats. It allows the user to also group players based on the custom stats they choose to evaluate players. Another option to use in this app is how stats picked are grouped together and groups are made for players that are similar with those stats. It is something similar with what I want to do with my project, but in this app, the stats that can be used are limited and I want to expand it with more. It is also only used for basketball players and I would expand it to other sports like baseball and football. 

Another work that is similar to my project is the website StatMuse ( \url{https://www.statmuse.com/}). The user can use key words to look up stats for a team or players across all sports in America. It displays the stats the the user was looking for in a chart after the website finds the specific stats. Examples of specific stats can be a specific player vs a team in their career, most point in a game in a specific year and much more. The website also has fantasy sport projections that users can ask the website. It will display a projection number in a chart for the player they want to know about. Compared to what I want to do, I would simplify this by not using keywords to look up stats and display graphs of the data that the user want to visualize.


\end{document}